Multiple Dice Working as One: CAD Flows and Routing Architectures for Silicon Interposer FPGAs

### 2015-07-01 doc/journal/fpgapaperfinal/FPGAPaper/response_to_reviewers.txt

[Javeed: fix.]

Some writing issues:

- Sec II.A, 1st paragraph, read "As described in Section III". It is a bit odd since the readers have not read section III at that point.

[Ehsan: take out.][DONE]

- The text never refers to Fig.3.
[Ehsan: add reference][DONE]

- There should not be indentation following eqts. (1), (2), (3), (5), (6).
[Ehsan: fix. Shouldn't start a new paragraph after.][DONE]

- Sec. V.E., "It is slightly worse ... even for ..." -> "But it is slightly worse ... for ..."
[Ehsan: fix.][DONE]

@@

Minor points:

Section I, third paragraph
- Don’t use [3] as a word. Either say “Ref. [3]” or “Alexander et al. [3]”
- et al should be “et al.” (there is a period after al, but not after et)

[Vaughn: fix]

Regarding the placer timing cost described in Section IV.A.1), does the delay term include the multiplexers or just the bumps and the wires through the interposer?
[Ehsan: modify text.][DONE]

Regarding Equation (3), can you give a better explanation of the W_chanx and W_chany terms? I didn’t completely understand them from the short 1-sentence description.
[Ehsan: change.][DONE]

Below Equation (6), I don’t understand the ratio_of_wires_cut metric, especially vis-a-vis Figure 6.
[Use % wires cut instead][DONE]

In Figure 6, the green box and label (a) are nearly impossible to see given the light blue background with white spacing. Please switch to a darker shade of green.
[Ehsan: fix][DONE]

In Equation (1), does the ExpectInterposeHops include the delay of the muxes?
[Ehsan: explain / fix][DONE: ExpectInterposeHops is not the delay term. It's the number of expected interposer hops which is multiplied by the total delay of each hop. I changed the variable name to: NumExpectedInterpHops]
